Supplementary Information

### 2020-03-10 writing/transect_supplement.Rmd
make a tree figure, add descriptions of supplementary files to the supplementary figures/tables file

**Supplementary file 1**:

>>>>

**Supplementary file 1**: Mapping between samples and indexed primers for short amplicons.

**Supplementary file 2**: Mapping between samples and indexed primers for long amplicons.

**Supplementary file 3**: ML tree of all long metabarcoding ASVs (5.8S--ITS2--LSU) assigned to kingdom Fungi.
Thick branches represent rapid bootstrap values >90%.
Taxonomic assignment by PHYLOTAX, based on assignments using RDPC, SINTAX, and IDTAXA, and Unite, Warcup, and RDP reference databases. 
Taxon names in blue were not fully resolved with PHYLOTAX, and are given as a list of alternative assignments, along with the number of methods which gave each assignment (max 9).
Taxon names in red were reconstructed as polyphyletic.
In some cases, this may be due to a poorly identified sequence "splitting" the group (e.g., the single *Aspergillus* sequence nested in *Monascus*, Aspergillaceae and Trichocomaceae sequences nested in Onygenales), but in other cases, the tree has clearly failed to reconstruct groups which are generally considered to be monophyletic based on multi-gene trees (e.g., Dothidiomycetes, Cantharellales).
